Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-04-03 documents/cpm.tex
discussion about cpm and other methods

In general, there are many reasons for apparent photometric variability in a \Kepler\ source.
There is intrinsic stellar variability,
  which is of interest to some and a nuisance to others.
There is also variability of overlapping fainter stars;
  that is, confusion noise combined with variability of the confusing sources.
There are small changes in spacecraft pointing,
  which leads to slightly different illumination of the focal-plane pixels,
  and thus different sensitivity to variations in the device.
There are also \emph{intra-pixel} sensitivity variations that can contribute \citep{whitepaper}.
There are small changes in spacecraft temperature,
  which lead to point-spread function (PSF) and differential (across the focal plane) pointing changes.
These also lead to changes in pixel and intra-pixel illumination.
Stellar proper motion, geometric parallaxes, and differential stellar aberration as the spacecraft orbits all do more of the same.
There is electronic cross-talk between detectors and charge-transfer inefficiency;
  these can effectively transfer variability from one source to another.
There are additional electronics effects like ``rolling bands'' that put additional features into lightcurves.
There are also probably changes to the detector sensitivity with temperature and time,
  possibly illimunation-history effects,
  and possibly sources of variability not yet considered.
The remarkable thing about \Kepler\ is that it is trying to measure stars at a level of precision
  much higher than ever previously attempted;
  new effects really \emph{must} appear at some point.
In \figurename~\ref{ccd}, we show the pixel-level variability in the \Kepler\ data
  near one bright star that shows minimal intrinsic variability;
  this figure highlights the spacecraft-induced effects.

@@

In \cite{pdc2,pdc3}, filtered light curves of other stars are used instead. 
The light curve of a target star is projected on the leading eight principal components of these light curves. 
This projection is then removed from the star's light curve. 
The principal components are computed from a set of relatively quiet stars close in position and magnitude. 
This was done since it was observed that otherwise, too much of the stellar variability was being removed.

@@

PDC ``de-trends'' the \Kepler\ lightcurves by removing those parts that are explained by the basis lightcurves
  generated from a principal components analysis (PCA) of filtered lightcurves.
That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) 
  by filtering and restricting the dimensionality (through PCA).

The method proposed here, \name, shares the motivation of PDC.
The main differences are that
\begin{enumerate}
\item
\name\ works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information
\item
\name\ has far more freedom (far more parameters) than the PDC
  but it strictly avoids over-fitting the lightcurves on exoplanet-transit time-scales
  through strong regularization and a train-and-test framework.
\item 
\name\ directly optimizes for prediction accuracy, while PDC uses PCA projections.
\item
the purpose of \name\ is to search for exoplanets, so in \name, intrinsic stellar
  variability is also removed as well as the systematics.
\item 
\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (lightcurves) of the other stars.
\end{enumerate}

The two methods (\name\ and PDC) are similar however,
  in that they both make the (implicit or explicit) assumption that whatever spacecraft effects are imprinting variability on a stellar lightcurve
  must also be imprinting similar or related variability on other lightcurves.
In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).
By going to the pixel level (unlike the PDC, which works at the photometry level),
  \name\ makes it easier for the model to capture variability
  that is coming through variations in the centroids and point-spread function
  from spacecraft pointing, roll, and temperature.

@@

The second general idea about data-driven modelling is the investigator's beliefs
  about the causal processes that generate the data
  are crucial in restricting the kinds of data that can be used as input to the model.
That is, different assumptions about the physical properties of the data
  and the data-taking system
  lead to different structures for the data-driven model.
In the case of \Kepler\ data, 
  if we examine two arbitrary stars far away from each other 
  on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light curve time series), 
  we can obviously see that the two stars that are hundreds pixel away from each other do have similar trends. 
  If we believe that different stars in the \Kepler\ field vary independently 
  (that is, are not physically synchronized in any way) because of the distance between them, 
  then the only reason that one star might show variability that is strongly \emph{predictive} (useful for prediction) of another star's variability
  is that both stars are being observed by the same device or spacecraft.
That is, one star's pixels can be used to predict another star's pixels
  inasmuch as spacecraft issues imprint on both stars in related ways;
  they share a common cause---the systematics.  
For another example, if we think the spacecraft is being affected by
  processes that take place over time-scales longer than a single read-out
  (for example, thermal processes),
  then it would be sensible to model the data at time $t$ using not just simultaneous data, but also data from a range of times around $t$.
For another example, if an investigator doesn't care about preserving stellar variability,
  and just wants to detect exoplanet transits (say),
  pixels from the target star can be used to predict pixels from the target star,
  provided they are at large-enough time lags that they don't contain information about
  the signals of interest (i.e., the transits).
That is, if the model is designed to fit not just spacecraft variability
  but also intrinsic stellar variability,
  the predictive model will be permitted to use as input pixels that \emph{do} overlap the 
  target star.
In what follows, we are going to use input data both from pixels of other stars and the  
target star pixels' past and future.
These models ought to remove both spacecraft variability and intrinsic stellar variability, 
which is optimal for exoplanet transit searching.

@@

Because of the train-and-test framework,  
  we expect the \name\ prediction $S_{n}$ to be a prediction of
  what the star lightcurve would have under the influence of the spacecraft but with no exoplanet signal 
Based on this idea, 
  we can construct the ``\name\ flux'' 
  (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved) 
  to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
\begin{eqnarray}
\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
\quad .
\end{eqnarray} 
In some sense, it is this relative residual--- the \name\ flux that contains the exoplanet transit signals we seek. 
That is, a transit creates a negative residual away from the prediction, 
  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).

@@

\subsection{Transit signal in \name}
One important feature of \name\ is that we use the train-and-test framework to preserve 
the transit signal. To show how well train-and-test framework performs, we make the
following experiments on \Kepler\ data as shown in Fig~\ref{distortion}
In the light curve of single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
with amplitude 1.0005 is inserted. To insert the signal, we simply multiply the light curve 
by the factor of 1.0005, which makes the little bump in the middle of the SAP light curve 
(black points in the first panel). With the distorted light curve, we both applied the 
\name\ and ordinary fitting to the data. In the result, we can see that both \name and 
ordinary fit the light curve quite well outside the range of inserted signal. However, 
when examine how these two models preserve the signal that we care, the ordinary
fitting fit out about 30 percent of the signal, while \name\ almost preserve the whole 
original amplitude. Therefore,  by this simple experiment, we are able to show that 
the train-and-test framework used here is capable to keep the transit signal with 
a particular time scale. And we want to emphasise that it is crucial for searching for
exoplanets, especially the small ones such as earth-like planets, which only have  
about tens of parts per million signal in the light curve.

@@

To give a view on how our method performs, \name\ is applied on several stars with 
known transit signals but different variability and magnitudes as shown in Fig.~\ref{fluxes}. 
From the plots, we can see that \name\ works quite well on these stars, producing the \name\ fluxes 
with low variation and preserving the transit signals.
In addition, \name\ and PDC are compared based on 6 quiet stars 
(non-variable stars, first two rows of Fig.~\ref{fluxes}). 
The results illustrate that for these quiet stars our approach removes 
a major part of the variability present in the PDC light curves, while preserving the transit signals. 
To provide a quantitative comparison, we ran \name\ on 1000 stars from the whole Kepler input catalog 
(500 chosen randomly from the whole list, and 500 random G-type sun-like stars), 
and estimate the Combined Differential Photometric Precision (CDPP,  \cite{cdpp1} )for \name\ and PDC. 
CDPP is an estimate of the relative precision in a time window, 
indicating the noise level seen by a transit signal with a given duration. 
The duration is typically chosen to be 3, 6, or 12 hours. 
We use the 12-hours CDPP metric, since the transit duration of an earth-like planet is roughly 10 hours. 
Before CDPP is estimated, the variability of the stars are evaluated by median differential variability 
  (MDV, see \cite{basri2013} for details). 
Based on the variability, the 100 most variable stars in the list are removed, 
  since PDC is not designed to remove stellar variability, 
  and we want to compare \name\ and PDC on the same footing.
Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, 
  showing that our method (\name) outperforms PDC.

@@

\section{Discussion}
We have presented a simple yet highly effective method---the \name\ that works in pixel-level 
  based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ lightcurves, 
  which is intended to search exoplanets.
In \name, systematics and stellar variabilities are removed by
  either fitting with other stars' lightcures or auto-regressive components,
  while transit signals can still be perfectly preserved by train-and-test framework.
Low variable clean lightcurves can be produced by \name\,  which is ideal for transit planet searching. 
The CDPP noise level estimation is also presented in the paper to show the performance of \name.

\todo{Compare with PDC, median filter, pre-whitening}

However, based on our assumption of the causal structure of the \Kepler\ data, 
  if we turn off the auto-regressive components and keep the predictors from other stars working in the \name, 
  we should be able to still remove the systematics while preserve the intrinsic stellar variability, 
  since there is no reason that these independent stars can be used to predict the stellar variability of the target star.
However, in fact, we can not preserve the stellar variability just by turning off the auto-regressive components. 
One possible reason can be that, since our model is so flexible (thousands of parameters), 
  in principle it can fit any functions. 
In this sense, 
  we should run cross-validation with the auto-regressive components turned off 
  and to find out how many pixels from other stars we need to just remove systematics 
  while preserve stellar variability, 
  but in fact we do not have a good criterion to check how well we preserve stellar variability in cross-validation 
  because we do not have enough knowledge of the true stellar variability. 
Thus for the time being, we just focus on producing well-calibrated light curves for searching exoplanets, 
  but in long term, we are looking forward to find a method to preserve the stellar variability.

Another issue of the \name\ is that when there are strong transit signals in the lightcurve,  
  one can find distortion around the these signals.
We think this problem is caused by the train-and-test framework.
Train-and-test framework is applied in the \name\ to preserve the transit signals, 
  in which data points in a certain excluded window are separated from the model.
However, for data points half-window size away from the transit signals, 
  the prediction of these points in \name\ is largely influenced by the strong transit signal.
That is,  these points are predicted to be a little bit smaller than they should be, 
  since transit signal (negative points away from the continuum) makes the model think
  there is a decreasing trend in this region.
This window edge effect is a trade-off of the train-and-test framework that is crucial for \name,
 and can not be solved in the scope of \name.

One possible way to solve this kind of edge effect 
  but still preserve the transit signals is to do the simultaneous fitting 
  for both systematics and transit signal together, 
  like what have been done in \cite{dfm}. 
That is,  
  instead of only modelling the systematics 
  and then subtracting it from the raw data to produce some de-trended lightcurves,
  a comprehensive model for all components in the data (systematics, stellar variabilities and transits)  can be made. In this kind of model, there is no need for train-and-test framework,
  since all transit signals have already been modelled 
  and no de-trended lightcurve will be produced. Planets will be found directly in the model itself.

>>>>

In general, there are many reasons for apparent photometric variability in a \Kepler\ source.
There is intrinsic stellar variability,
  which is of interest to some and a nuisance to others.
There is also variability of overlapping fainter stars;
  that is, confusion noise combined with variability of the confusing sources.
There are small changes in spacecraft pointing,
  which leads to slightly different illumination of the focal-plane pixels,
  and thus different sensitivity to variations in the device.
There are also \emph{intra-pixel} sensitivity variations that can contribute \citep{whitepaper}.
There are small changes in spacecraft temperature,
  which lead to point-spread function (PSF) and differential (across the focal plane) pointing changes.
These also lead to changes in pixel and intra-pixel illumination.
Stellar proper motion, geometric parallaxes, and differential stellar aberration as the spacecraft orbits all do more of the same.
There is electronic cross-talk between detectors and charge-transfer inefficiency;
  these can effectively transfer variability from one source to another.
There are additional electronics effects like ``rolling bands'' that put additional features into light-curves.
There are also probably changes to the detector sensitivity with temperature and time,
  possibly illimunation-history effects,
  and possibly sources of variability not yet considered.
The remarkable thing about \Kepler\ is that it is trying to measure stars at a level of precision
  much higher than ever previously attempted;
  new effects really \emph{must} appear at some point.
In \figurename~\ref{ccd}, we show the pixel-level variability in the \Kepler\ data
  near one bright star that shows minimal intrinsic variability;
  this figure highlights the spacecraft-induced effects.

@@

In \cite{pdc2,pdc3}, filtered light-curves of other stars are used instead. 
The light-curve of a target star is projected on the leading eight principal components of these light-curves. 
This projection is then removed from the star's light-curve. 
The principal components are computed from a set of relatively quiet stars close in position and magnitude. 
This was done since it was observed that otherwise, too much of the stellar variability was being removed.

@@

PDC ``de-trends'' the \Kepler\ light-curves by removing those parts that are explained by the basis light-curves
  generated from a principal components analysis (PCA) of filtered light-curves.
That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) 
  by filtering and restricting the dimensionality (through PCA).

The method proposed here, \name, shares the motivation of PDC.
The main differences are that
\begin{enumerate}
\item
\name\ works in the pixel domain, not the light-curve domain, so it has access to more fine-grained information
\item
\name\ has far more freedom (far more parameters) than the PDC
  but it strictly avoids over-fitting the light-curves on exoplanet-transit time-scales
  through strong regularization and a train-and-test framework.
\item 
\name\ directly optimizes for prediction accuracy, while PDC uses PCA projections.
\item
the purpose of \name\ is to search for exoplanets, so in \name, intrinsic stellar
  variability is also removed as well as the systematics.
\item 
\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (light-curves) of the other stars.
\end{enumerate}

The two methods (\name\ and PDC) are similar however,
  in that they both make the (implicit or explicit) assumption that whatever spacecraft effects are imprinting variability on a stellar light-curve
  must also be imprinting similar or related variability on other light-curves.
In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).
By going to the pixel level (unlike the PDC, which works at the photometry level),
  \name\ makes it easier for the model to capture variability
  that is coming through variations in the centroids and point-spread function
  from spacecraft pointing, roll, and temperature.

@@

The second general idea about data-driven modelling is the investigator's beliefs
  about the causal processes that generate the data
  are crucial in restricting the kinds of data that can be used as input to the model.
That is, different assumptions about the physical properties of the data
  and the data-taking system
  lead to different structures for the data-driven model.
In the case of \Kepler\ data, 
  if we examine two arbitrary stars far away from each other 
  on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light-curve time series), 
  we can obviously see that the two stars that are hundreds pixel away from each other do have similar trends. 
  If we believe that different stars in the \Kepler\ field vary independently 
  (that is, are not physically synchronized in any way) because of the distance between them, 
  then the only reason that one star might show variability that is strongly \emph{predictive} (useful for prediction) of another star's variability
  is that both stars are being observed by the same device or spacecraft.
That is, one star's pixels can be used to predict another star's pixels
  inasmuch as spacecraft issues imprint on both stars in related ways;
  they share a common cause---the systematics.  
For another example, if we think the spacecraft is being affected by
  processes that take place over time-scales longer than a single read-out
  (for example, thermal processes),
  then it would be sensible to model the data at time $t$ using not just simultaneous data, but also data from a range of times around $t$.
For another example, if an investigator doesn't care about preserving stellar variability,
  and just wants to detect exoplanet transits (say),
  pixels from the target star can be used to predict pixels from the target star,
  provided they are at large-enough time lags that they don't contain information about
  the signals of interest (i.e., the transits).
That is, if the model is designed to fit not just spacecraft variability
  but also intrinsic stellar variability,
  the predictive model will be permitted to use as input pixels that \emph{do} overlap the 
  target star.
In what follows, we are going to use input data both from pixels of other stars and the  
target star pixels' past and future.
These models ought to remove both spacecraft variability and intrinsic stellar variability, 
which is optimal for exoplanet transit searching.

@@

Because of the train-and-test framework,  
  we expect the \name\ prediction $S_{n}$ to be a prediction of
  what the star light-curve would have under the influence of the spacecraft but with no exoplanet signal 
Based on this idea, 
  we can construct the ``\name\ flux'' 
  (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved) 
  to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
\begin{eqnarray}
\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
\quad .
\end{eqnarray} 
In some sense, it is this relative residual--- the \name\ flux that contains the exoplanet transit signals we seek. 
That is, a transit creates a negative residual away from the prediction, 
  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).

@@

\subsection{Transit signal in \name}
One important feature of \name\ is that we use the train-and-test framework to preserve 
the transit signal. To show how well train-and-test framework performs, we make the
following experiments on \Kepler\ data as shown in Fig~\ref{distortion}
In the light-curve of single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
with amplitude 1.0005 is inserted. To insert the signal, we simply multiply the light-curve 
by the factor of 1.0005, which makes the little bump in the middle of the SAP light-curve 
(black points in the first panel). With the distorted light-curve, we both applied the 
\name\ and ordinary fitting to the data. In the result, we can see that both \name and 
ordinary fit the light-curve quite well outside the range of inserted signal. However, 
when examine how these two models preserve the signal that we care, the ordinary
fitting fit out about 30 percent of the signal, while \name\ almost preserve the whole 
original amplitude. Therefore,  by this simple experiment, we are able to show that 
the train-and-test framework used here is capable to keep the transit signal with 
a particular time scale. And we want to emphasise that it is crucial for searching for
exoplanets, especially the small ones such as earth-like planets, which only have  
about tens of parts per million signal in the light-curve.

@@

To give a view on how our method performs, \name\ is applied on several stars with 
known transit signals but different variability and magnitudes as shown in Fig.~\ref{fluxes}. 
From the plots, we can see that \name\ works quite well on these stars, producing the \name\ fluxes 
with low variation and preserving the transit signals.
In addition, \name\ and PDC are compared based on 6 quiet stars 
(non-variable stars, first two rows of Fig.~\ref{fluxes}). 
The results illustrate that for these quiet stars our approach removes 
a major part of the variability present in the PDC light-curves, while preserving the transit signals. 
To provide a quantitative comparison, we ran \name\ on 1000 stars from the whole Kepler input catalog 
(500 chosen randomly from the whole list, and 500 random G-type sun-like stars), 
and estimate the Combined Differential Photometric Precision (CDPP,  \cite{cdpp1} )for \name\ and PDC. 
CDPP is an estimate of the relative precision in a time window, 
indicating the noise level seen by a transit signal with a given duration. 
The duration is typically chosen to be 3, 6, or 12 hours. 
We use the 12-hours CDPP metric, since the transit duration of an earth-like planet is roughly 10 hours. 
Before CDPP is estimated, the variability of the stars are evaluated by median differential variability 
  (MDV, see \cite{basri2013} for details). 
Based on the variability, the 100 most variable stars in the list are removed, 
  since PDC is not designed to remove stellar variability, 
  and we want to compare \name\ and PDC on the same footing.
Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, 
  showing that our method (\name) outperforms PDC.

@@

\section{Discussion}
We have presented a simple yet highly effective method---the \name\ that works in pixel-level 
  based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ light-curves, 
  which is intended to search exoplanets.
In \name, systematics and stellar variabilities are removed by
  either fitting with other stars' light-curves or auto-regressive components,
  while transit signals can still be perfectly preserved by train-and-test framework.
Low variable clean light-curves can be produced by \name\,  
  which is ideal for transit planet searching. 
The CDPP noise level estimation is also presented in the paper to show the performance of \name.

Apart from the \name, as mentioned in the beginning of the paper, 
  there exist several other methods that are effective in de-trending the light-curve.
Methods like median filter are quite successful in smoothing all the unwanted features 
  either from spacecraft or intrinsic stellar variability, 
  but the problem is that this kind of methods filter everything in the data including the transit signal. 
This is not a big deal for searching giant planets, since the signal is quite strong. 
However, 
  when it comes to earth-like planets (only about 20 ppm transit signal around a sun-like star),
  any reduction or distortion of the signal is unacceptable. 
In comparison, in order to achieve higher precision for earth-like planet searching, 
  \name\  not only exploits the causal structure of the \Kepler\ data,
  but also apply effective approaches (strong regularization and train-and-test framework)
  to avoid over-fitting the transit signal.
There also exists more sophisticated method like PDC.
As mentioned earlier in this paper, 
  \name\ is very similar to PDC, 
  in that they both make use of the correlation between light-curves,
  which is assumed to be caused by the spacecraft effects (or systematics).
However, in section 4, we show that \name\ performs better than PDC, 
  in that it has a overall low noise level (CDPP).
We think the outperformance mainly caused by two factor.
One is that \name\ calibrates every single pixel separately, 
  while PDC works in the photometry level.
It is no doubt that pixel-level modelling enables \name\ capture more variability, such as 
variations in the centroids and point-spread function from spacecraft pointing, roll, and temperature.
The other reason is that,  
  in PDC,  only leading eight principal components of some relative light-curves are used.
Although restricting the number of components can prevent over-fitting, we think with this limited number of components, 
  it is insufficient to capture all the variabilities in the light-curve.
In \name\, hundreds of stars' light-curves (or thousands of pixels) are used 
  to capture relatively complete information of the variabilities, 
  while strong regularization and train-and-test framework are applied to prevent over-fitting.
Although we present the comparison between \name\ and PDC, 
  we still want to emphasis that PDC is a method intended to preserve stellar variabilities, 
  while the \name\ is optimized for exoplanet searching. 
The comparison is only based on our objective (search for earth-like planet), 
  and should not be regard as standard of a best model for \Kepler\ data.

However, apart from the outstanding performance in calibrating the data,  
  the \name\ still has several issues. 
Based on our assumption of the causal structure of the \Kepler\ data, 
  if we turn off the auto-regressive components and keep the predictors from other stars working in the \name, 
  we should be able to still remove the systematics while preserve the intrinsic stellar variability, 
  since there is no reason that these independent stars can be used to predict the stellar variability of the target star.
However, in fact, we can not preserve the stellar variability just by turning off the auto-regressive components. 
One possible reason can be that, since our model is so flexible (thousands of parameters), 
  in principle it can fit any functions. 
In this sense, 
  we should run cross-validation with the auto-regressive components turned off 
  and to find out how many pixels from other stars we need to just remove systematics 
  while preserve stellar variability, 
  but in fact we do not have a good criterion to check how well we preserve stellar variability in cross-validation 
  because we do not have enough knowledge of the true stellar variability. 
Thus for the time being, we just focus on producing well-calibrated light-curves for searching exoplanets, 
  but in long term, we are looking forward to find a method to preserve the stellar variability.

Another issue of the \name\ is that when there are strong transit signals in the light-curve,  
  one can find distortion around the these signals.
We think this problem is caused by the train-and-test framework.
Train-and-test framework is applied in the \name\ to preserve the transit signals, 
  in which data points in a certain excluded window are separated from the model.
However, for data points half-window size away from the transit signals, 
  the prediction of these points in \name\ is largely influenced by the strong transit signal.
That is,  these points are predicted to be a little bit smaller than they should be, 
  since transit signal (negative points away from the continuum) makes the model think
  there is a decreasing trend in this region.
This window edge effect is a trade-off of the train-and-test framework that is crucial for \name,
 and can not be solved in the scope of \name.

One possible way to solve this kind of edge effect 
  but still preserve the transit signals is to do the simultaneous fitting 
  for both systematics and transit signal together, 
  like what have been done in \cite{dfm}. 
That is,  
  instead of only modelling the systematics 
  and then subtracting it from the raw data to produce some de-trended light-curves,
  a comprehensive model for all components in the data (systematics, stellar variabilities and transits)  can be made. In this kind of model, there is no need for train-and-test framework,
  since all transit signals have already been modelled 
  and no de-trended light-curve will be produced. Planets will be found directly in the model itself.
